Perturbing SU($n$)-symmetric interactions

### 2020-03-17 collective_sun/sun_perturbation.tex
fixed minor notational inconsistency

Symmetries of $H_0$ and $\V_M$ essentially break the set of choices
$\C_N\p{M}$ into equivalence classes $\S\p{M}$\footnote{For brevity,
  we will suppress the explicit dependence of $\S\p{M}$ on $N$, as
  well as the dependence of $\S\p{M}$ on any other factors such as
  lattice geometry.}, where elements $s\in\S\p{M}$ are subsets
$s\subset\C_N\p{M}$ that are invariant under the appropriate symmetry
group action.  In the case of a translationally invariant and
isotropic system with two-body perturbations, for example, each
equivalence class $s\in\S_2$ would consist of all pairs
$\p{p,q}\in\C_N\p{2}$ that are a fixed distance $\abs{p-q}=d_s$ apart,
i.e.~$s=\set{\p{p,q}\in\C_N\p{2}:\abs{p-q}=d_s}$.

Our task is essentially to express the multi-body eigenvalue problem
in \eqref{eq:H_VM_psi_eig} in a basis that obeys the symmetries under
consideration.  To this end, for any equivalence class $s\in\S\p{M}$
we define a uniform superposition $\ket{s}$ over all choices $k\in s$,
as well as the projector $\P_\S$ onto the space of uniform
superpositions:
\begin{align}
  \ket{s} \equiv \f1{\sqrt{\abs{s}}} \sum_{k\in s} \ket{k},
  &&
  \P_{\S_M} \equiv \sum_{s\in\S\p{M}} \op{s},
\end{align}
where $\abs{s}$ is the number of elements in $s$.  We then expand the
coefficient vector $\v{\m w}$ in this symmetrized basis:
\begin{align}
  \v{\m w} = \sum_{k\in\C_N\p{M}} w_k \ket{k}
  = \sum_{s\in\S_M} w_s \sqrt{\abs{s}} \ket{s},
\end{align}
where $w_s\equiv w_k$ for any $k\in s$.  Finally, we define the
projection of $\check{\m h}$ onto the symmetric subspace:
\begin{align}
  \check{\m h}_{\S_M}
  \equiv \P_{\S_M} \check{\m h} \P_{\S_M}
  = \sum_{s\in\S_M} \ket{s} \sp{
    \sum_{k\in s} \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{a\in\ZZ_M}
    \f{h_{p k_a}}{\sqrt{\abs{s}\abs{\sp{k_{a:p}}}}} \bra{\sp{k_{a:p}}}
    - \tilde h_s \bra{s}},
\end{align}
where $\tilde h_s\equiv \tilde h_k$ for any $k\in s$; $k_a$ is the
$a$-th element of $k$;
$k_{a:p}\equiv\p{k_1,k_2,\cdots,k_{a-1},p,k_{a+1},\cdots,k_M}$ is $k$,
but with the $a$-th number $k_a$ replaced by $p$; and $\sp{k_{a:p}}$
is the equivalence class of $k_{a:p}$.  The reduced multi-body
eigenvalue problem is then
\begin{align}
  \check{\m h}_{\S_M} \c \v{\m w} = \Delta \v{\m w}.
\end{align}

>>>>

Symmetries of $H_0$ and $\V_M$ essentially break the set of choices
$\C_N\p{M}$ into equivalence classes $\S_M$\footnote{For brevity, we
  will suppress the explicit dependence of $\S_M$ on $N$, as well as
  the dependence of $\S_M$ on any other factors such as lattice
  geometry.}, where elements $s\in\S_M$ are subsets
$s\subset\C_N\p{M}$ that are invariant under the appropriate symmetry
group action.  In the case of a translationally invariant and
isotropic system with two-body perturbations, for example, each
equivalence class $s\in\S_2$ would consist of all pairs
$\p{p,q}\in\C_N\p{2}$ that are a fixed distance $\abs{p-q}=d_s$ apart,
i.e.~$s=\set{\p{p,q}\in\C_N\p{2}:\abs{p-q}=d_s}$.

Our task is essentially to express the multi-body eigenvalue problem
in \eqref{eq:H_VM_psi_eig} in a basis that obeys the symmetries under
consideration.  To this end, for any equivalence class $s\in\S_M$ we
define a uniform superposition $\ket{s}$ over all choices $k\in s$, as
well as the projector $\P_\S$ onto the space of uniform
superpositions:
\begin{align}
  \ket{s} \equiv \f1{\sqrt{\abs{s}}} \sum_{k\in s} \ket{k},
  &&
  \P_{\S_M} \equiv \sum_{s\in\S_M} \op{s},
\end{align}
where $\abs{s}$ is the number of elements in $s$.  We then expand the
coefficient vector $\v{\m w}$ in this symmetrized basis:
\begin{align}
  \v{\m w} = \sum_{k\in\C_N\p{M}} w_k \ket{k}
  = \sum_{s\in\S_M} w_s \sqrt{\abs{s}} \ket{s},
\end{align}
where $w_s\equiv w_k$ for any $k\in s$.  Finally, we define the
projection of $\check{\m h}$ onto the symmetric subspace:
\begin{align}
  \check{\m h}_{\S_M}
  \equiv \P_{\S_M} \check{\m h} \P_{\S_M}
  = \sum_{s\in\S_M} \ket{s} \sp{
    \sum_{k\in s} \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{a\in\ZZ_M}
    \f{h_{p k_a}}{\sqrt{\abs{s}\abs{\sp{k_{a:p}}}}} \bra{\sp{k_{a:p}}}
    - \tilde h_s \bra{s}},
\end{align}
where $\tilde h_s\equiv \tilde h_k$ for any $k\in s$; $k_a$ is the
$a$-th element of $k$;
$k_{a:p}\equiv\p{k_1,k_2,\cdots,k_{a-1},p,k_{a+1},\cdots,k_M}$ is $k$,
but with the $a$-th number $k_a$ replaced by $p$; and $\sp{k_{a:p}}$
is the equivalence class of $k_{a:p}$.  The reduced multi-body
eigenvalue problem is then
\begin{align}
  \check{\m h}_{\S_M} \c \v{\m w} = \Delta \v{\m w}.
\end{align}
